High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-19 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$40\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source. The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 4.17$\pm$0.94\,au. Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disk. Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprising thin Ring13 is nonetheless 15 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.

@@

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S. Perez). These were acquired in the context of the DARTTS-A program (Perez et al. {\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution. The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz). This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs06$ (in natural weights). **Seba, sure that the survey only used C43-8?***

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs04 \, \times \, 0\farcs06$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs01 \, \times \, \sim0\farcs02$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$. For all the images in the figure the colour scale is linear.}
  \label{fig:two}
\end{figure*}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig. \ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs01 \, \times \, \sim0\farcs02$), the ring width is $\sim$3.99$\pm$0.94\,au.

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig. \ref{fig:two}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:***} below). If so, then given that the binary phase at the time of the observations is PA=***, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image shown in Fig. \ref{fig:two} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches  the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 360-106\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 360-13\,$\degr$. There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a  mutual separation of 0.041\,au, so that their center of mass coincides with the origin,  and oriented at a PA of *****  30\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi****  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi} **** GIVE ORIENTATION IN TERMS OF THE PA****

@@

The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=***$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$. The small dust density is thus given by 
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
\end{equation}
***I changed $f_{\mathrm{sd}}$  to $f_{\mathrm{sd}}$. say how much is $f_{sd}$.

Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and   scaling factors that account for  the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two    Gaussian profiles. In an effort to recreate the break seen in the outer ring between 32 and 34.5\,au, we chose a different value for $\gamma$ = -8. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

***REWORD PARA, IT IS NOT CLEAR WHERE DOES THIS EPSILON ENTERS - IF IT IS COMMON TO BOTH SPECIES, THEN INCLUDE IT IN THE GAS PROFILE. I DID NOT CHECK REDACTION, MAKE THIS AS COMPACT AS POSSIBLE***  Also for both dust populations, the inner part of the outer ring follows a different behaviour. The surface density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

@@

Through trial and error, we found a set of values for the parameters that  correctly fit the available data. The final structure of the parametric model goes as Fig. \ref{fig:profiles} shows. The inner radius of the model grid was set to 0.1\,au and an outter radius of 115\,au, large enough for the dust disc to become undetectable.

The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$****. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS  observations but was required to account for the  SED. Then follow the two  rings observed by IRDIS:  Ring13, from 12 to 19.5\,au, which is surrounded by very narrow  1\,au-wide gap, and then Ring24, that starts  20.5\,au and has its maximum density peak at 25\,au. The small-dust density  then decays exponentially with  radius.

On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 12.3$\,au), a narrow 2.6\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap  that separates the  outer ring (Ring24), which starts at  23\,au and reaches peak  densities  at 27.3\,au. This last ring has an observed break between 32 and 34.5\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials. We also truncated  the model large-grain density at  $\sim$57\,au.

@@

The simulated 1.3\,mm continuum image  reproduces the two observed rings: the faint Ring13 and the  brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 2.6\,au, and a  scale height ranging from 0.25 to 0.32\,au. The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.  In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then  breaks  at $\sim$35\,au, as in the observations, and has a total dust  mass of $\sim$43\,M$_{\earth}$.

****DISCUTIR EL ANCHO OBSERVADO VS. ANCHO MODELO****

As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent ***HOW MUCH SMALLER?***. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.

***CHECK THAT THE RT PREDICTIONS USE THE SAME BEAM FOR CONVOLUTION AS THE DATA, AND UPDATE ALL FIGURES****

@@

The observed SED is compared with the model in Fig. \ref{fig:SED}. From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit ***WHERE in LBDA?****, and we may have detected this ring in the ALMA image, if this ring is  lopsided or shadowed by the secondary.

@@

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model.  The key conclusions are as follows.
\begin{enumerate}

\item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 4.17$\pm$0.94\,au **UPDATE FOR NEW BEAM***. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height ***UPDATE****

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au. 
  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars ***IS THIS NOT A CONFIRMATION OF THE INNER DIST PROPOSED BY ROSENFELD+? IF SO, SAY SO****. We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and  that lies under the coronagraph of the scattered-light image. The weak central emission at 1.3\,mm could be part of this ring.
\end{enumerate}

>>>>

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source. The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au. Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disk. Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprising thin Ring13 is nonetheless 15 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.

@@

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S. Perez). These were acquired in the context of the DARTTS-A program (Perez et al. {\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution. The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz). This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights). ***Seba, sure that the survey only used C43-8?***

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$. For all the images in the figure the colour scale is linear.}
  \label{fig:two}
\end{figure*}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig. \ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.87$\pm$0.94\,au.

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig. \ref{fig:two}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image shown in Fig. \ref{fig:two} also shows a double ring structure in the micron-
sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$. There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a  mutual separation of 0.041\,au, so that their centre of mass coincides with the origin,  and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi***  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.

@@

The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=0.01$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$. The small dust density is thus given by 
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
\end{equation}

Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for  the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two    Gaussian profiles. In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

The inner part of the outer ring follows a different behaviour. The gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

@@

Through trial and error, we found a set of values for the parameters that  correctly fit the available data. The final structure of the parametric model goes as Fig. \ref{fig:profiles} shows. The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.

The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS  observations but was required to account for the  SED. Then follow the two  rings observed by IRDIS:  Ring13, from 12 to 19.5\,au, which is surrounded by very narrow  1\,au-wide gap, and then Ring24, that starts  20.5\,au and has its maximum density peak at 25\,au. The small-dust density  then decays exponentially with  radius.

On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.8$\,au), a narrow 3.6\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au. This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials. We also truncated  the model large-grain density at  $\sim$55\,au.

@@

The simulated 1.3\,mm continuum image  reproduces the two observed rings: the faint Ring13 and the  brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 3.6\,au, and a  scale height ranging from 0.24 to 0.32\,au. The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.  In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then  breaks  at $\sim$35\,au, as in the observations, and has a total dust  mass of $\sim$43\,M$_{\earth}$.

****DISCUTIR EL ANCHO OBSERVADO 3.87 VS. ANCHO MODELO 3.6 ****

As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$13 times its scale height.

@@

The observed SED is compared with the model in Fig. \ref{fig:SED}. From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$***, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.

@@

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model.  The key conclusions are as follows.
\begin{enumerate}
  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 3.87$\pm$0.94\,au. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$13 times its estimated height.

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.

  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars. We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and  that lies under the coronagraph of the scattered-light image. The weak central emission at 1.3\,mm could be part of this ring.
\end{enumerate}
